% resume.tex
% vim:set ft=tex spell:

\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Jamison Dance}}

345 N 400 E\ \ \textbullet
\ \ Orem, UT 84049
\\
(801) 709-0325\ \ \textbullet
\ \ jamison.d.dance@gmail.com
\\
\ \ \url{http://jamisondance.com} \ \ \textbullet
\ \ \url{http://github.com/jergason}
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Prince Lab, Brigham Young University}}
		{\textbf{Provo, UT}}
	\\
	\headerrow
		{\emph{Software Developer \& Research Assistant}}
		{\emph{2010 -- Present}}
	\begin{itemize*}
		\item Designed and developed a Ruby on Rails web application to expose
			scientific data via a RESTful API. See \url{http://github.com/jergason/pocketbook}.
		\item Designed and developed a Rails application that allows interactive
			metrics tracking for a mass spectrometer. See 
			\url{http://github.com/princelab/rails-metric_site}.
		\item Designed web-based tools to help with scheduling time on scientific
			instruments, ensuring the instrument is used efficiently at all times.
		\item Provided training on programming and basic Linux skills to scientists with
			no previous computing experience.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Computer Science Department, Brigham Young University}}
		{\textbf{Provo, UT}}
	\\
	\headerrow
		{\emph{Department Webmaster}}
		{\emph{2008 - 2010}}
	\begin{itemize*}
		\item Developed a Drupal module to manage graduate student profiles,
		significantly speeding up the graduate student review process.
		\item Maintained and updated custom employment system written in PHP
		to track several hundred student employees.
		\item Developed a Drupal module to synchronize content across multiple Drupal
		sites and social networks to allow centralized publication to several different
		destinations.
		\item Trained two new webmasters in PHP and Drupal development.
	\end{itemize*}

	\headerrow
		{\textbf{Freelance Developer}}
		{\emph{2010 - Present}}
	\begin{itemize*}
		\item Turned photoshop templates into Drupal themes and wrote several custom Drupal
			modules for a truck sales website at \url{http://heavytruckswholesale.com}.
		\item Designed, developed, and deployed a web application to allow a company to give automatic
			quotes for used trucks based on the mileage and VIN at \url{http://earlycre.com}.
	\end{itemize*}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Brigham Young University}}
		{\textbf{Provo, UT}}
	\\
	\headerrow
		{\emph{College of Physical and Mathematical Science, B.S. Computer Science, Bioinformatics}}
		{\emph{2012}}
	\begin{itemize*}
		\item Class experience includes network programming, software development, data structures.
		\item Received a four year academic scholarship.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	Ruby, PHP, JavaScript,  HTML, CSS, Python, SQL, Java, \CPP, C, \LaTeX
	\item[Other Skills:]
	Git, Subversion, Linux
	\item[Proof of Said Skills:]
	\href{http://github.com/jergason}{Github}, \href{http://stackoverflow.com/users/78093/jergason}{StackOverflow}
\end{description*}
\end{indentsection}

\end{document}
